The five axes of the Turtle: symmetry and asymmetry in NGC~6210

### 2020-10-04 ms.tex
Deal with referee query about inner shell

Along axis~B,
which is the apparent minor axis of the inner shell (\(\pm 5''\)),
the ellipse is distorted and the gradient is much more pronounced:
\(\pm \SI{11}{km.s^{-1}}\),
with the more negative velocities at the ENE end
(large blue circle symbols in lower panel of Fig.~\ref{fig:shell-velocity-axes}).
Velocity splitting of \(\pm \SI{9}{km.s^{-1}}\) is seen near both ends,
but it is not clear from the \oiii{} spectra if the ends are closed or open,
since none of the \oiii{} slits are aligned with this axis.
However, one of the \nii{} slits (slit~w) is indeed oriented close to axis~B and,
although the shell emits only weakly in \nii{},
the distorted ellipse is clearly closed at the ENE end
(large pink triangle symbol in Fig.~\ref{fig:shell-velocity-axes}).
The situation is not so clear at the WSW end
since any \nii{} emission from the shell is swamped by brighter emission from the knot complexes.
However, the evidence from \textit{HST} imaging suggests that the shell is closed in this direction also.

>>>>

Along axis~B,
which is the apparent minor axis of the inner shell (\(\pm 5''\)),
the ellipse is distorted and the gradient is much more pronounced:
\(\pm \SI{11}{km.s^{-1}}\),
with the more negative velocities at the ENE end
(large blue circle symbols in lower panel of Fig.~\ref{fig:shell-velocity-axes}).
Velocity splitting of \(\pm \SI{9}{km.s^{-1}}\) is seen near both ends,
but it is not clear from the \oiii{} spectra if the ends are closed or open,
since none of the \oiii{} slits are aligned with this axis.
However, one of the \nii{} slits (slit~w) is indeed oriented close to axis~B and,
although the shell emits only weakly in \nii{},
the distorted ellipse is clearly closed at the ENE end
(large pink triangle symbol in Fig.~\ref{fig:shell-velocity-axes}).
The situation is not so clear at the WSW end
since any \nii{} emission from the shell is swamped by brighter emission from the knot complexes.
However, the evidence from \textit{HST} imaging suggests that the shell may be closed in this direction also (indicated by thin dashed blue line in the lower panel of Fig.~\ref{fig:shell-velocity-axes}).
